Machine Learning rooted Potential piloted RRT* for expeditious Path Planning

### 2018-12-18 Research Paper/paper.tex

\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
% \usepackage{amsmath}
% \usepackage{mathtools}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{algorithm}
\caption{RRT*}\label{RRT*}
\begin{algorithmic}[1]
\Procedure{rrt_star}{$T(v,e), Z_{init}$}
\State $T\gets InsertNode(\phi,Z_{init},T);$
\For{$i = 1, 2, ..., N \do $}
\State $Z_{rand}\gets Sample(i);$
\State $Z_{nearest}\gets Nearest(T,Z_{rand});$
\State $(Z_{nearest},U_{new} )\gets Steer(Z_{nearest},Z_{rand});$
\If{$Obstaclefree(Z_{new})$}
\State $Z_{near}\gets Near(T,Z_{new},V);$
\State $Z_{min}\gets Chooseparent(Z_{near},Z_{nearest},Z_{new});$
\State $T\gets InsertNode(Z_{min},Z_{new},T);$
\State $T\gets Rewire(T,Z_{near},Z_{min},Z_{new});$
\EndFor
\EndIf
\State\hspace{-5mm} \textbf{return} $T$
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\subsubsection{Potential field}
The potential field generated can be compared to an electrostatic field. The obstacles are assumed to be positively charged, and the destination to be negatively charged. This places the obstacles at a relatively higher positive potential. The aim is to descend towards lower potential as much as possible. All charges are taken as point charges. At every point $x$ in the space, the potential is calculated for a particular charge as $\text{V_{i}}=\frac{\text{kQ_{i}}}{\text{r_{i}}}$ where $Q_{i}$ is the magnitude of the $i^{th}$ point charge (obstacle or destination), and $r_{i}$ is the distance of the point $x$ from it. The net potential at a point is given by $\sum_{i=1}^{n} V_{i} = k\sum_{i=1}^{n} \frac{\text{Q_{i}}}{\text{r_{i}}}$. Here $k$ is a proportionality constant, and $n$ is the total number of charges. We determine the values of $Q$ and $k$ by validation.

The sampling method used in the RT-RRT*\cite{RT-RRT*} to generate new nodes is applicable here as well. Briefly, a random number between 0 and 1 is generated, and on the basis of that, it is determined where random sampling is to be performed. $LineTo(x_{goal})$ is invoked when the random number generated is greater than $1 - \alpha$, else if the number is less than $\frac{1-\alpha}{\beta}$  $Uniform(X)$ is invoked. Otherwise  $Ellipsis(x_{0},x_{goal})$ is called. Here $\beta$ is a real number used for making a distinction between the last two function calls. Next, taking inspiration from PGD-RRT*\cite{PG-RRT}, the randomly generated point is allowed to descend according to the potential gradient for a certain amount of time. The resulting point is treated as the initially generated node for an RRT*. The best parent to this node is determined within the surrounding grids of the node. From that parent, at a particular step length, the new node is created. The entire procedure, in a nutshell, is provided in the Algorithm 3.

% \begin{figure}
% \includegraphics[width=\textwidth]{images2_3_new.jpeg}
% \begin{center}
% \caption{Wavefronts due to robot while stationary and while moving. This is described mathematically by the Doppler Effect. Along the violet line, the (a) frequency graph, (b) the potential graph and (c) the overall graph have been shown} \label{fig1}
% \end{center}
% \end{figure}

% \vspace{-5mm}  
% \begin{algorithm}
% \caption{Random sampling}\label{alg:RandomSampling}
% \begin{algorithmic}[1]
% \Procedure{Random sampling}{$U$, $G$, $\alpha$, $\beta$, $\gamma$, $step$\textunderscore$size$}\Comment{Graph $G$ is the existing graph, Field $U$ is the generated field}
% \State $A\gets {rand(0,1)}$ \Comment{Random number generation between 0 and 1.}
% \If {$A \geq 1 - \alpha$}
% \State $x_{rand} = LineTo(x_{goal})$ 
% \Else
%   \If {$\frac{1-\alpha}{\beta}$}
%   \State $x_{rand} = Uniform(X)$
%   \Else  
%     \State $x_{rand} = Ellipsis(x_{0},x_{goal})$
%   \EndIf
% \EndIf
% \State $x_{parent} = BestParent(x_{rand})$\Comment{Best parent is decided as per the recursive cost function}
% \State $x_{random} = NodeAtDist(Angle(x_{parent}, x_{rand}), step$\textunderscore$size)$ \Comment{Finding the node on the line joining $x_{parent}$ and $x_{rand}$ at a distance $step$\textunderscore$size$ from $x_{parent}$}
% \State $x_{final} = x_{random} - \gamma \frac{\delta(U)}{\delta(x)}|_{x = x_{final}}$
% \State $U = AddToGraph(U, x_{final})$
% \If {Graph has been saturated}
%   \State return
% \Else
%   \State $RANDOMSAMPLING(U, G, \alpha, \beta, \gamma, \step$\textunderscore$size$)
% \EndIf
% \EndProcedure
% \end{algorithmic}
% \end{algorithm}

% \subsection{Hexagonal grid}
% \vspace{-2mm}
% The entire area is divided into a set of grids, and all the nodes are mapped to a specific grid. In another way, every node is assigned a particular grid ID, which is developed in such a manner that the entire area gets divided into a set of hexagonal grids. Hexagon ensures most efficient packing in 2D space and is quite popular in path planning domain \cite{apna}. The potentials developed correspond to those of the points at the centres of the respective grids. 
% \vspace{-3mm}
% \subsection{Edge rewiring}
% \vspace{-2mm}
% The RT-RRT* proposes to rewire edges under three categories. We explain the changes we make to each of them:
% \vspace{-5mm}
% \subsubsection{Rewire in the presence of an obstacle:}
% When a path is being approached by an obstacle, a rewiring is necessary. According to the RT-RRT* algorithm, any path which goes through the obstacles attain infinite cost. Similarly, when obstacles have charge, they provide an infinite potential at their point of existence. Hence, both of them seamlessly integrate with one another. But, here, the infinite potential is assumed for a greater radius, as deemed fit for the situation. Accordingly, rewiring is prioritised in such regions.
% \vspace{-5mm}
% \subsubsection{Rewire from root:}
% Rewiring begins at the root and keeps proceeding throughout the tree. Hence, it starts rewiring from the position where the agent lies. Then, it continues to assign nodes which are at greater distance from the agent to their corresponding best-matching parents.
% \vspace{-5mm}
% \subsubsection{Random rewiring:}
% This paper proposes to remove random rewiring from RT-RRT* and introduces a way of determining edges which are to be rewired. At every point of the field, these wavefronts would be perceivable. In case the robot is moving, the frequency detected at a point would be different from that of what had been emitted. This is known as the Doppler Effect. The frequency due to Doppler effect is expressed as $f = \left(\frac{v + v_r}{v + v_s}\right)f_0$ where $f$ is the perceived frequency, $f_{0}$ is the constant frequency emitted by obstacles, $v$ is the constant velocity of wave in space, $v_r$ is receiver's velocity and $v_s$ is the source's velocity which will be equal to the obstacle's velocity in our case. The frequency at every point in the field is calculated using 
% \begin{align}
% \sin(\omega_1t)+\sin(\omega_2t)
% &=2\sin\left(\frac{\omega_1+\omega_2}{2}t\right)\cos\left(\frac{\omega_1-\omega_2}{2}t\right)
% \end{align}

% \noindent in a binary fashion. This has been illustrated in Fig 2(a). Thus, we obtain the net frequency of every point in the field. After plotting this across the field, we obtain the local minima. Finding out the maximum among these local minima, we rewire edges randomly in that grids.

% \subsection{Boundary Conditions}
% An exponential potential control barrier function is defined in 3D space. Let the boundary of the field/environment be defined by $\displaystyle{\textbf{B(x)}}$ and let \textbf{x\textsubscript{b}} be a point on the boundary. The growth of the potential function around boundary is defined by   $B(x) = \frac{1}{1-e^{-||x_b-x||}}$.
% Thus, the potential field around the boundary of the environment proliferates as,
% \vspace{-2mm}
% \begin{center}
%   $\lim_{x \rightarrow x_b}\frac{1}{1-e^{-||x_b-x||}}\rightarrow\infty$ 
% \end{center}
% % \vspace{-2mm}
% $||x||$ represents $x^T.x$.
% A moving body incident on the barrier gets reflected, and hence would restrict path generation.

% \section{Cost function}
% % incorporate distance velocity and acceleration\\
% % distance using potential field\\
% % velocity using doppler's effect\\
% % acceleration using energy lost\\

% The cost function in the RT-RRT*\cite{RT-RRT*} algorithm is used to find the best parent of a node while performing edge-rewiring. Edge rewiring, as described in previous sections, helps in optimising an already generated path, by providing nodes with better parents. The RT-RRT* defines cost recursively as:
% \vspace{-2mm}
% \begin{equation}
%     cost_{distance}({x_{new}}) = cost(x_{closest}) + dist(x_{closest}, x_{new})
% \end{equation}
% Where $x_{new}$ is the node for which we wish to compute the cost, $x_{closest}$ is the node closest to $x_{new}$ and $dist(x_{closest}, x_{new})$ is the distance between $x_{new}$ and $x_{closest}$. This paper proposes to make some changes to the existing cost function, making PGD-RRT* suitable for a dynamic environment. The recursive approach to the cost function remains the same. The difference lies in the way the distance (using $dist$) is computed. Hence $x_{closest}$ shall be modified as well. Nevertheless, $x_{closest}$ remains the closest node via the distance metric, but in this paper, we attempt to replace the commonly used Euclidean distance with geodesic distance. The two-dimensional graph of the area initially developed using an artificial potential field is taken into consideration. The straight line path which gives the Euclidean distance between $x_{new}$ and $x_{closest}$ is projected on this graph. The length of the curve thus obtained is taken as the distance. Thus, the formula remains the same, but the approach to computing the distance is a bit different. It is explained in a better fashion through the illustration provided (Fig 1).

% Let the potential surface be represented as $\vec{S}$ and the position vectors of the points $x_{closest}$ and $x_{new}$ be $\vec{a}$ and $\vec{b}$. The distance is measured along the curve formed by intersection of $\vec{S}$ with a plane which is parallel to the z axis and passes through the straight line path between $\vec{a}$ and $\vec{b}$.  We assign $\hat{n}$ to be the cross product between $\vec{a} - \vec{b}$ and a unit vector along the z axis. We obtain a plane $\vec{P}$ as $(\vec{r} - \vec{a}) \cdot \hat{n} = 0$, where $\vec{r}$ is an arbitrary point on the plane.  Thus, the curve formed along the path between two nodes becomes \vec{C}: $ \vec{S} - \vec{P}  = \textbf{0} $. $dist(x_{closest}, x_{new})$ is the arclength along $\vec{C}$ from $\vec{a}$ to $\vec{b}$. If we represent $\vec{C}$ parametrically as $\vec{p}(t)$ =  $<x(t), y(t), z(t)>$ with $t_{1}$ and $t_{2}$ being the parametric values for $\vec{a}$ and $\vec{b}$, then the arclength is given by
% \begin{center}
%     $dist(x_{closest}, x_{new}) = \int_{t_{1}} ^ {t_{2}} \sqrt{ \left ( \frac{dx}{dt} \right )^2 + \left ( \frac{dy}{dt} \right )^2 + \left ( \frac{dz}{dt} \right )^2} \: dt$
% \end{center}
% \vspace{-6mm}
% % Various costs have been computed considering different parameters as:
% % \\

% % Distance Cost($C_1$) : \\

% % Velocity Cost($C_2$) : \\

% % Accleration Cost($C_3$) : \\
% % \\
% % For finding optimal path a combined cost function($C$) has been used which is computed using the above three cost functions as: \\

% % $C = \alpha * C_1 + \beta * C_2 + \gamma * C_3$

% \subsubsection{Doppler Effect} The cost function incorporates the velocity using the Doppler effect. This accounts for the dynamic nature of obstacles. The shift in frequency helps in the prediction of approach/separation of the body concerning obstacles.
% The frequency at every point in the field is calculated by superimposition of waves from all the obstacles, as illustrated in Fig 2. This shift in frequency is plotted on  a two dimensional axis for all obstacles. The obtained map explains the relative velocity of approach/separation of obstacles with respect to the moving body.
% \vspace{-2mm}
% \begin{equation}
%  \displaystyle \mathbf{F}(\mathbf {\hat{x}},t) = \sum_{i=0}^{|obstacles|}{f_{i}}
% \end{equation}

% where, $|obstacles|$ represents the cardinality of the obstacle vector, $\displaystyle{f_{i}}$ denotes the observed frequency of $\mathbf{i}_{th}$ obstacle and $t$ is time.
% The surface so obtained corresponds to obstacles' activity. The minima on the surface correspond to low activity regions of obstacles. To extract the local minima the surface is descended iteratively.
% ${\displaystyle \mathbf {x} _{n+1}=\mathbf {x} _{n}-\gamma _{n}\nabla F(\mathbf {x} _{n}),\ n\geq 0.}$
% where \textbf{x\textsubscript{n}} are points in Cartesian plane with \textbf{x\textsubscript{0}} as initial guess. To ensure convergence  step size ${\displaystyle \gamma }$ is kept small. However an effective ${\displaystyle \gamma }$ via Barzilai-Borwein method \cite{BB} yields promising results.The Barzilai-Borwein method is shown below \\
% \vspace{-2mm}
% \begin{equation}
% {\displaystyle \gamma _{n}={\frac {(\mathbf {x} _{n}-\mathbf {x} _{n-1})^{T}[\nabla F(\mathbf {x} _{n})-\nabla F(\mathbf {x} _{n-1})]}{||\nabla F(\mathbf {x} _{n})-\nabla F(\mathbf {x} _{n-1})||^{2}}}}    
% \end{equation}
% \vspace{-2mm}
% The cost is defined as
% % unable to align
% \vspace{-2mm}
% \begin{equation}
% cost_{velocity}(x_{new}) = \lambda| \textbf{F}(\hat{\textbf{x}},t)|_{at \hspace{2pt} \textbf{x} = x_{new}}
% \end{equation}\vspace{-4mm}\\
% where $\lambda$ is a constant close to unity. Thus, low activity regions would be associated with low costs.
% Effective or total cost is computed as a linear combination of given by,
% % unable to align
% \vspace{-2mm}
% \begin{equation}
% cost(x) = c_{0} cost_{distance}(\textbf{x}) + c_{1}  cost_{velocity}(\textbf{x})
% \end{equation}
% Where $c_{0}$ and $c_{1}$ are two constants which depend on the environment and can be tuned to achieve promising results. Incorporating boundary condition would change effective cost to
% \begin{center}
%     $cost(x)_{effective} = cost(x) B(x)$
% \end{center}\vspace{-4mm}
% \begin{algorithm}
% \caption{Rewiring random edges}\label{alg:Rewirin}
% \begin{algorithmic}[1]
% \Procedure{Rewire random}{$U$, $G$, $D$, $grid$, $\epsilon$, $root$}\Comment{Graph $G$ is the existing graph, Field $U$ is the generated field}
% \State $F = U + \epsilon D$
% \State $grid_{min} = rand(1,length(grid))$
% \State $max$\textunderscore$min = grid_{min}$
% \For {each $i$; $i$ in $length(grid)$}
% \State $flag = False$
%     \If{$F[i]< F$[each $neighbour$ of $grid[i]$]}
%         \If{$max$\textunderscore$min < F[i]$}
%           $max$\textunderscore$min < F[i]$
%         \EndIf
%     \EndIf
% \EndFor
% \State $cost_{org} = cost(Parent(max$\textunderscore$min), max$\textunderscore$min)$
% \State $node_{final} = max$\textunderscore$min$
% \For {each node $i$ in current and neighbouring grids}
%     \State $cost_{here} = cost(i,max$\textunderscore$min) + cost(i, root)$
%     \If{$cost_{here} < cost_{org}$}
%       \State $cost_{org} = cost_{here}$
%       \State $node_{final} = i$
%     \EndIf
% \EndFor
% \State $max$\textunderscore$min.setParent = node_{final}$
% \EndProcedure
% \end{algorithmic}
% \end{algorithm}

% \section{Experimentation and Analysis}
% \begin{figure}
% \begin{center}
% \includegraphics[scale=0.3]{image_2.png}
%  \caption{The simulation environment, showing (a) our path planner and (b) RT-RRT*} \label{fig1}
% \end{center}
% \end{figure}

% We conducted an experiment based on tree generation time given a set of obstacles. The experimental setup included ROS based communication nodes and a GUI based interactive platform for setting up the environment. This was performed on Linux 4.4.0-127-generic with 8 GiB memory and 2.3 GHz x 8 CPU.
% % \vspace{-1mm}
% \begin{table}[]
% \centering
% \caption{Comparison of time (in milli seconds) in generation of path}
% \label{Comparison with other planners}
% \begin{tabular}{@{}c|@{\hskip 0.1in}cccl@{}}
% \toprule
% \multirow{\textbf{Obstacles}} & \multicolumn{4}{c}{\textbf{Average Traversal Time}}              
% \\
%  & \textbf{PGD-RRT*} & \textbf{RRT*} & \textbf{RT-RRT*} & \textbf{Our planner} \\
%  \hline
% 5 & 4.1996  &  3.7078  &  3.7951  & 2.7958\\
% 7 & 4.2315  &  3.7912  &  3.8105  & 2.8110\\
% 9 & 4.2555  &  3.9105  &  3.8492  & 2.8862\\
% 10 & 4.2658 &  3.9824  &  3.8908  & 2.8873\\
% 12 & 4.3655 &  4.1473  &  4.1335  & 3.1080\\
% 15 & 4.4662 &  4.2194  &  4.3264  & 3.1866\\
% 18 & 4.6905 &  4.4505  &  4.5155  & 3.4242\\
% 20 & 4.9696 &  4.9191  &  4.9583  & 3.9823\\ 
% \end{tabular}
% \vspace{-6mm}
% \end{table}
% Thus, it can be seen that our planner takes nearly the same time to generate the tree given similar set of environmental conditions. Along with that, our planner provides a more optimised path. The average number of iterations required to find the path to each goal was 10.36 for our method and 18.43 for RT-RRT*.\\
% \vspace{-6mm}
% \subsubsection{Replanning}
% In a dynamic environment, the replanning of path is an important aspect. Moving obstacles when come along the path, a new path has to be found incorporating the new position of the obstacles. For better performance of agents, this replanning of path should take place in less amount of time. Our proposed path planner outperforms other planners in this, hence making it suitable for a real-time dynamic environment. With respect to the PGD-RRT*, our path planner is very quick in replanning as the tree growth does not take place again and again, but gets rewired when required. With respect to the RT-RRT*, our planner provides a more optimised path, which is clear from the illustration provided (fig 3) and Table 1. Our planner is based on a dynamic environment only and can be outperformed by other planners in a static environment.

>>>>

\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\setcounter{secnumdepth}{2}
% \usepackage{amsmath}
% \usepackage{mathtools}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{algorithm}
\caption{RRT*}\label{RRT*}
\begin{algorithmic}[1]
\Procedure{rrt\_star}{$T(v,e), Z_{init}$}
\State $T\gets InsertNode(\phi,Z_{init},T);$
\For{$i = 1, 2, ..., N \do $}
\State $Z_{rand}\gets Sample(i);$
\State $Z_{nearest}\gets Nearest(T,Z_{rand});$
\State $(Z_{nearest},U_{new} )\gets Steer(Z_{nearest},Z_{rand});$
\If{$Obstaclefree(Z_{new})$}
\State $Z_{near}\gets Near(T,Z_{new},V);$
\State $Z_{min}\gets Chooseparent(Z_{near},Z_{nearest},Z_{new});$
\State $T\gets InsertNode(Z_{min},Z_{new},T);$
\State $T\gets Rewire(T,Z_{near},Z_{min},Z_{new});$
\EndIf
\EndFor
\State\textbf{return} $T$
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\subsection{Potential field:}
Electrostatic field is a very  coarse-grained approximation of the potential field generated in the field. It is clearly evident that the destination should made to act like a positive charge and attract the tree to grow towards it. But since the obstacles should be avoided and hence they should be made to act like negative charges and repel the tree. At every point $x$ in the space, the potential is calculated for a particular charge as $\text{V_{i}}=\frac{\text{kQ_{i}}}{\text{r_{i}}}$ where $Q_{i}$ is the magnitude of the $i^{th}$ point charge (obstacle ), and $r_{i}$ is the distance of the point $x$ from it. The net potential at a point is given by :

\vspace{3mm}
$\sum_{i=1}^{n}V_{i}=k\sum_{i=1}^{n}\frac{\text{Q_{i}}}{\text{r_{i}}} + \text{k^\prime}\frac{\text{Q^\prime}}{\text{r^\prime}}$
\vspace{3mm}

\hspace{-5mm}Here $k$ and $k^\prime$ is a proportionality constant due to obstacles and destination respectively, and $n$ is the total number of charges.

Now how much the tree should grow towards the destination relative to growing away from the obstacles, dependant on $k$ and $k^\prime$ is a very sensitive parameter and has serious implications.
\vspace{3mm}

\subsection{Ideal Path and Potential Constants:}
To find the ideal constants of potential field , we first found the ideal path by using BFS and Dijkstra and then reverse engineered our way to find the ideal potential functions for over 100,000 images

\begin{figure}
\begin{center}
\includegraphics[scale=1]{images2.png}
    \caption{The above image shows the ideal path to calculate the ideal path using BFS and Dijkstra.} \label{fig1}
\end{center}
\end{figure}

\subsection{Training:}
We took the centres of the each obstacle blob and the total area of the obstacles as the features and trained it with the potential using Random Forest Regressor model on around 100,000 images randomly generated images.

% \begin{figure}
% We conducted an experiment based on tree generation time given a set of obstacles. The experimental setup included ROS based communication nodes and a GUI based interactive platform for setting up the environment. This was performed on Linux 4.4.0-127-generic with 8 GiB memory and 2.3 GHz x 8 CPU.
% % \vspace{-1mm}
% \begin{table}[]
% \centering
% \caption{Comparison of time (in milli seconds) in generation of path}
% \label{Comparison with other planners}
% \begin{tabular}{@{}c|@{\hskip 0.1in}cccl@{}}
% \toprule
% \multirow{\textbf{Obstacles}} & \multicolumn{4}{c}{\textbf{Average Traversal Time}}              
% \\
%  & \textbf{PGD-RRT*} & \textbf{RRT*} & \textbf{RT-RRT*} & \textbf{Our planner} \\
%  \hline
% 5 & 4.1996  &  3.7078  &  3.7951  & 2.7958\\
% 7 & 4.2315  &  3.7912  &  3.8105  & 2.8110\\
% 9 & 4.2555  &  3.9105  &  3.8492  & 2.8862\\
% 10 & 4.2658 &  3.9824  &  3.8908  & 2.8873\\
% 12 & 4.3655 &  4.1473  &  4.1335  & 3.1080\\
% 15 & 4.4662 &  4.2194  &  4.3264  & 3.1866\\
% 18 & 4.6905 &  4.4505  &  4.5155  & 3.4242\\
% 20 & 4.9696 &  4.9191  &  4.9583  & 3.9823\\ 
% \end{tabular}
% \vspace{-6mm}
% \end{table}
% Thus, it can be seen that our planner takes nearly the same time to generate the tree given similar set of environmental conditions. Along with that, our planner provides a more optimised path. The average number of iterations required to find the path to each goal was 10.36 for our method and 18.43 for RT-RRT*.\\
% \vspace{-6mm}
% \subsubsection{Replanning}
% In a dynamic environment, the replanning of path is an important aspect. Moving obstacles when come along the path, a new path has to be found incorporating the new position of the obstacles. For better performance of agents, this replanning of path should take place in less amount of time. Our proposed path planner outperforms other planners in this, hence making it suitable for a real-time dynamic environment. With respect to the PGD-RRT*, our path planner is very quick in replanning as the tree growth does not take place again and again, but gets rewired when required. With respect to the RT-RRT*, our planner provides a more optimised path, which is clear from the illustration provided (fig 3) and Table 1. Our planner is based on a dynamic environment only and can be outperformed by other planners in a static environment.
